Growing libraries of concepts with wake-sleep program induction

### 2018-07-19 talk.tex
beautiful table
Added figures

>>>>

\begin{frame}[t]{EC}
  \includegraphics[width = 11cm]{figures/animation/EC.eps}
\end{frame}
\begin{frame}[t]{DC}
  \includegraphics[width = 11cm]{figures/animation/DC.eps}
\end{frame}
\begin{frame}[t]{Wake}
  \includegraphics[width = 11cm]{figures/animation/Wake.eps}
\end{frame}
\begin{frame}[t]{Sleep-G}
  \includegraphics[width = 11cm]{figures/animation/Sleep-G.eps}
\end{frame}
\begin{frame}[t]{Sleep-R-1}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}
\end{frame}
\begin{frame}[t]{Sleep-R-2}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}
